We are not the 99 percent: quantifying asphericity in the Local Group satellites' distributions

### 2017-11-03 paper/paper.tex
text +pdf

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG as an outlier]{We are not the 99 percent: quantifying
  bright satellite distributions in the Local Group}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

Finally,

In Section we list the sources of the observational and
simulated data to be used throughout the paper.
Next, in Section we describe the methods we use to quantify and
characterize the satellite distributions.
In section we present our results. 
In the discussion section we quantify the correlations between the main
plane properties as described by the simulations.
We use this results to quantify the degree of atipicality of the LG
and estimate the volume that has to probed in simulations in order to
find a pair with a satellite distribution as atipical as the LG. 
Finally, we summarize our conclusions in Section .

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellites asphericity ]{We are not the 99 percent: quantifying
  asphericity in the Local Group satellites' distributions}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

Finally, to compute the odds of finding the LG satellite distributions 
in LCDM simulations, we do not make a direct search for the exact
observed values into simulations because, as we show in Section, the
LG is itself rare and we do not have enough simulated systems to
perform such a brute force solution. 
We also avoid this direct comparison for a second reason. 
We do not want to implicitly use either LCDM or observations as what
is considered normal or standard and compute the deviations from that
point. 
Our approach is different. 
We set as a point of reference an spherical satellite
distribution to quantify how both simulations and observations
deviate from the spherical distribution.
Simulations help us to construct an explicit probability distribution
for deviations from sphericity in LCDM.
Then we compute the odds of finding n satellite distributions that
deviates from sphericity as much as the LG does.

In Section we list the sources of the observational and
simulated data to be used throughout the paper.
Next, in Section we describe the methods we use to quantify and
characterize the satellite distributions.
In section we present the results. 
In the discussion section we quantify the correlations between the main
plane properties as described by the simulations.
We use this results to quantify the degree of atipicality of the LG
and estimate the volume that has to probed in simulations in order to
find a pair with a satellite distribution as atipical as the LG. 
Finally, we summarize our conclusions in Section .
